A Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}

### 2019-05-26 main.tex
General descripltion on evaluation contexts.

At the end of definition section, we define values, a staged reduction, and evaluation contexts of \LMD.

>>>>

The reduction given above is a full reduction and any redexes can be reduced in arbitrary order.
But we need to fix a order of reduction when we implement a interpreter of \LMD and
the order must be appropriate in terms of stages.

We will define deterministic call-by-value staged semantics which can be used as a basis of a \LMD\ interpreter.
In this reduction, $\longrightarrow_\beta$ and $\longrightarrow_\Lambda$ are allowed only at stage $\epsilon$ and 
$\longrightarrow_\blacklozenge$ is allowed only at stage $\alpha$.
